### 2018-03-02 submission/manuscript.Rmd
complete discussion section with pat suggestions

Meta analysis are important (eg. obesity, crc), we need more. We learned that these are hard because…
Inaccessible datasets
Missing/vague metadata
Varying sequence quality
Small datasets

>>>>

Despite these limitations the findings that we present here would not be possible without performing a meta-analysis. These types of studies can be a useful tool in microbiota research because they can both validate existing research and make new discoveries by pooling many independent investigations together. Yet, it is still difficult to perform these studies because of inaccessible 16S sequencing data, missing or vague metadata (e.g. which samples are carcioma and which are not), varying sequence quality, and multiple small data sets. Better attention to these specific problems could help to increase the reproducibility and replicability of microbiota studies and make it easier to perform these crucial meta-analyses. Moving forward, meta-analyses will be important tools to help aggregate and find commonalities across studies when investigating the microbiota in the context of a specific disease and more are needed [@Sze2016; @Walters2014; @Finucane2014; @shah_leveraging_2017].

### 2018-03-02 submission/manuscript.tex
complete discussion section with pat suggestions

Meta analysis are important (eg. obesity, crc), we need more. We learned
that these are hard because\ldots{} Inaccessible datasets Missing/vague
metadata Varying sequence quality Small datasets

@@

\textbf{\emph{Obtaining Data Sets:}} The studies used for this
meta-analysis were identified through the review articles written by
Keku, \emph{et al.} and Vogtmann, \emph{et al.} (38, 39) and additional
studies not mentioned in the reviews were obtained based on the authors'
knowledge of the literature. Studies that used tissue or feces as their
sample source for 454 or Illumina 16S rRNA gene sequencing analysis and
had data sets with sequences available for analysis were included. Some
studies were excluded because they did not have publicly available
sequences or did not have metadata in which the authors were able to
share. After these filtering steps, the following studies remained: Ahn,
\emph{et al.} (11), Baxter, \emph{et al.} (12), Brim, \emph{et al.}
(29), Burns, \emph{et al.} (15), Chen, \emph{et al.} (13), Dejea,
\emph{et al.} (20), Flemer, \emph{et al.} (17), Geng, \emph{et al.}
(19), Hale, \emph{et al.} (27), Kostic, \emph{et al.} (40), Lu, \emph{et
al.} (26), Sanapareddy, \emph{et al.} (25), Wang, \emph{et al.} (14),
Weir, \emph{et al.} (23), and Zeller, \emph{et al.} (16). The Zackular
(41) study was not included because the 90 individuals analyzed within
the study are contained within the larger Baxter study (12). After
sequence processing, all the case samples for the Kostic study had 100
or less sequences remaining and was excluded, leaving a total of 14
studies that analysis could be completed on.

@@

\textbf{\emph{Sequence Processing:}} For the majority of studies, raw
sequences were downloaded from the Sequence Read Archive (SRA)
(\url{ftp://ftp-trace.ncbi.nih.gov/sra/sra-instant/reads/ByStudy/sra/SRP/})
and metadata were obtained by searching the respective accession number
of the study at the following website:
\url{http://www.ncbi.nlm.nih.gov/Traces/study/}. Of the studies that did
not have sequences and metadata on the SRA, data was obtained from DBGap
(n = 1, (11)) and directly from the authors (n = 4, (17, 23, 25, 27)).
Each study was processed using the mothur (v1.39.3) software program
(42) and quality filtering utilized the default methods for both 454 and
Illumina based sequencing. If it was not possible to use the defaults,
the stated quality cut-offs, from the study itself, were used instead.
Sequences that were made up of an artificial combination of two or more
different sequences and commonly known as chimeras were identified and
removed using VSEARCH (43) before \emph{de novo} OTU clustering at 97\%
similarity was completed using the OptiClust algorithm (44).

\textbf{\emph{Study Analysis Overview:}} OTU richness, evenness, and
Shannon diversity were first assessed for differences between controls,
adenoma tumors, and carcinoma turmors using both linear mixed-effect
models and ORs. For each individual study the Bray-Curtis index was used
to assess differences between control-adenoma and control-carcinoma
individuals. Next, all common genera were assessed for differences in
ORs for individuals having an adenoma or carcinoma and corrected for
multiple comparisons using the Benjamini-Hochberg method (45). We then
built Random Forest models based on all genera, all OTUs, or significant
OR taxa (only using taxa still significant after multiple comparison
correction). For both the full genera and significant OR taxa, models
were trained on one study then tested on the remaining studies using
genera-based relative abundances. The OTU-based models were built using
OTU level data and a 10-fold CV over 100 different iterations, based on
random 80/20 splitting of the data, was used to generate a range of
expected AUCs. This process was repeated for every study in the
meta-analysis. Comparisons of the initial trained model AUCs for the
full genera and significant OR taxa were made to the mean AUC generated
from the 100 different 10-fold CV runs of the respective OTU-based
model. For comparisons in which only control versus adenoma individuals
were made, the carcinoma individuals were excluded from each respective
study. Similarly, for comparisons in which control versus carcinoma
individuals were made the adenoma individuals were excluded from each
respective study. For all analysis completed fecal and tissue samples
were kept separate. Within the tissue groups the data were further
divided between samples from the same individual (matched) and those
from different individuals (unmatched).

@@

\textbf{\emph{Statistical Analysis:}} All statistical analysis after
sequence processing utilized the R (v3.4.3) software package (46). For
OTU richness, evenness, and Shannon diversity analysis, values were
power transformed using the rcompanion (v1.11.1) package (47) and then
Z-score normalized using the car (v2.1.6) package (48). Testing for OTU
richness, evenness, and Shannon diversity differences utilized linear
mixed-effect models created using the lme4 (v1.1.15) package (49) to
correct for study, repeat sampling of individuals (tissue only), and 16S
hyper-variable region used. Odds ratios (OR) were analyzed using both
the epiR (v0.9.93) and metafor (v2.0.0) packages (50, 51) by assessing
how many individuals with and without disease were above and below the
overall median value within each specific study. OR significance testing
utilized the chi-squared test. Diversity differences measured by the
Bray-Curtis index utilized the creation of distance matrix and testing
with PERMANOVA executed with the vegan (v2.4.5) package (52). Random
Forest models were built using both the caret (v6.0.78) and randomForest
(v4.6.12) packages (53, 54). All figures were created using both ggplot2
(v2.2.1) and gridExtra (v2.3) packages (55, 56).

@@

\hypertarget{ref-keku_gastrointestinal_2015}{}
38. \textbf{Keku, T. O.}, \textbf{S. Dulal}, \textbf{A. Deveaux},
\textbf{B. Jovov}, and \textbf{X. Han}. 2015. The gastrointestinal
microbiota and colorectal cancer. American Journal of Physiology -
Gastrointestinal and Liver Physiology \textbf{308}:G351--G363.

\hypertarget{ref-vogtmann_epidemiologic_2016}{}
39. \textbf{Vogtmann, E.}, and \textbf{J. J. Goedert}. 2016.
Epidemiologic studies of the human microbiome and cancer. British
Journal of Cancer \textbf{114}:237--242.

\hypertarget{ref-kostic_genomic_2012}{}
40. \textbf{Kostic, A. D.}, \textbf{D. Gevers}, \textbf{C. S.
Pedamallu}, \textbf{M. Michaud}, \textbf{F. Duke}, \textbf{A. M. Earl},
\textbf{A. I. Ojesina}, \textbf{J. Jung}, \textbf{A. J. Bass},
\textbf{J. Tabernero}, \textbf{J. Baselga}, \textbf{C. Liu}, \textbf{R.
A. Shivdasani}, \textbf{S. Ogino}, \textbf{B. W. Birren}, \textbf{C.
Huttenhower}, \textbf{W. S. Garrett}, and \textbf{M. Meyerson}. 2012.
Genomic analysis identifies association of Fusobacterium with colorectal
carcinoma. Genome Research \textbf{22}:292--298.

\hypertarget{ref-zackular_human_2014}{}
41. \textbf{Zackular, J. P.}, \textbf{M. A. M. Rogers}, \textbf{M. T.
Ruffin}, and \textbf{P. D. Schloss}. 2014. The human gut microbiome as a
screening tool for colorectal cancer. Cancer Prevention Research
(Philadelphia, Pa.) \textbf{7}:1112--1121.

\hypertarget{ref-schloss_introducing_2009}{}
42. \textbf{Schloss, P. D.}, \textbf{S. L. Westcott}, \textbf{T.
Ryabin}, \textbf{J. R. Hall}, \textbf{M. Hartmann}, \textbf{E. B.
Hollister}, \textbf{R. A. Lesniewski}, \textbf{B. B. Oakley}, \textbf{D.
H. Parks}, \textbf{C. J. Robinson}, \textbf{J. W. Sahl}, \textbf{B.
Stres}, \textbf{G. G. Thallinger}, \textbf{D. J. Van Horn}, and
\textbf{C. F. Weber}. 2009. Introducing mothur: Open-Source,
Platform-Independent, Community-Supported Software for Describing and
Comparing Microbial Communities. Appl.Environ.Microbiol.
\textbf{75}:7537--7541.

\hypertarget{ref-rognes_vsearch_2016}{}
43. \textbf{Rognes, T.}, \textbf{T. Flouri}, \textbf{B. Nichols},
\textbf{C. Quince}, and \textbf{F. Mahé}. 2016. VSEARCH: A versatile
open source tool for metagenomics. PeerJ \textbf{4}:e2584.

\hypertarget{ref-westcott_opticlust_2017}{}
44. \textbf{Westcott, S. L.}, and \textbf{P. D. Schloss}. 2017.
OptiClust, an Improved Method for Assigning Amplicon-Based Sequence Data
to Operational Taxonomic Units. mSphere \textbf{2}.

\hypertarget{ref-benjamini_controlling_1995}{}
45. \textbf{Benjamini, Y.}, and \textbf{Y. Hochberg}. 1995. Controlling
the false discovery rate: A practical and powerful approach to multiple
testing. Journal of the Royal Statistical Society. Series B
(Methodological) \textbf{57}:289--300.

\hypertarget{ref-r_citation_2017}{}
46. \textbf{R Core Team}. 2017. R: A language and environment for
statistical computing. R Foundation for Statistical Computing, Vienna,
Austria.

\hypertarget{ref-rcompanion_citation_2017}{}
47. \textbf{Mangiafico, S.} 2017. Rcompanion: Functions to support
extension education program evaluation.

\hypertarget{ref-car_citation_2011}{}
48. \textbf{Fox, J.}, and \textbf{S. Weisberg}. 2011. An R companion to
applied regressionSecond. Sage, Thousand Oaks CA.

\hypertarget{ref-lme4_citation_2015}{}
49. \textbf{Bates, D.}, \textbf{M. Mächler}, \textbf{B. Bolker}, and
\textbf{S. Walker}. 2015. Fitting linear mixed-effects models using
lme4. Journal of Statistical Software \textbf{67}:1--48.

\hypertarget{ref-epir_citation_2017}{}
50. \textbf{Telmo Nunes, M. S. with contributions from}, \textbf{C.
Heuer}, \textbf{J. Marshall}, \textbf{J. Sanchez}, \textbf{R. Thornton},
\textbf{J. Reiczigel}, \textbf{J. Robison-Cox}, \textbf{P. Sebastiani},
\textbf{P. Solymos}, \textbf{K. Yoshida}, \textbf{G. Jones}, \textbf{S.
Pirikahu}, \textbf{S. Firestone}, and \textbf{R. Kyle.} 2017. EpiR:
Tools for the analysis of epidemiological data.

\hypertarget{ref-metafor_citation_2010}{}
51. \textbf{Viechtbauer, W.} 2010. Conducting meta-analyses in R with
the metafor package. Journal of Statistical Software \textbf{36}:1--48.

\hypertarget{ref-vegan_citation_2017}{}
52. \textbf{Oksanen, J.}, \textbf{F. G. Blanchet}, \textbf{M. Friendly},
\textbf{R. Kindt}, \textbf{P. Legendre}, \textbf{D. McGlinn}, \textbf{P.
R. Minchin}, \textbf{R. B. O'Hara}, \textbf{G. L. Simpson}, \textbf{P.
Solymos}, \textbf{M. H. H. Stevens}, \textbf{E. Szoecs}, and \textbf{H.
Wagner}. 2017. Vegan: Community ecology package.

\hypertarget{ref-caret_citation_2017}{}
53. \textbf{Jed Wing, M. K. C. from}, \textbf{S. Weston}, \textbf{A.
Williams}, \textbf{C. Keefer}, \textbf{A. Engelhardt}, \textbf{T.
Cooper}, \textbf{Z. Mayer}, \textbf{B. Kenkel}, \textbf{the R Core
Team}, \textbf{M. Benesty}, \textbf{R. Lescarbeau}, \textbf{A. Ziem},
\textbf{L. Scrucca}, \textbf{Y. Tang}, \textbf{C. Candan}, and
\textbf{T. Hunt.} 2017. Caret: Classification and regression training.

\hypertarget{ref-randomforest_citation_2002}{}
54. \textbf{Liaw, A.}, and \textbf{M. Wiener}. 2002. Classification and
regression by randomForest. R News \textbf{2}:18--22.

\hypertarget{ref-ggplot2_citation_2009}{}
55. \textbf{Wickham, H.} 2009. Ggplot2: Elegant graphics for data
analysis. Springer-Verlag New York.

\hypertarget{ref-gridextra_citation_2017}{}
56. \textbf{Auguie, B.} 2017. GridExtra: Miscellaneous functions for
``grid'' graphics.

>>>>

Despite these limitations the findings that we present here would not be
possible without performing a meta-analysis. These types of studies can
be a useful tool in microbiota research because they can both validate
existing research and make new discoveries by pooling many independent
investigations together. Yet, it is still difficult to perform these
studies because of inaccessible 16S sequencing data, missing or vague
metadata (e.g.~which samples are carcioma and which are not), varying
sequence quality, and multiple small data sets. Better attention to
these specific problems could help to increase the reproducibility and
replicability of microbiota studies and make it easier to perform these
crucial meta-analyses. Moving forward, meta-analyses will be important
tools to help aggregate and find commonalities across studies when
investigating the microbiota in the context of a specific disease and
more are needed (28, 38--40).

@@

\textbf{\emph{Obtaining Data Sets:}} The studies used for this
meta-analysis were identified through the review articles written by
Keku, \emph{et al.} and Vogtmann, \emph{et al.} (41, 42) and additional
studies not mentioned in the reviews were obtained based on the authors'
knowledge of the literature. Studies that used tissue or feces as their
sample source for 454 or Illumina 16S rRNA gene sequencing analysis and
had data sets with sequences available for analysis were included. Some
studies were excluded because they did not have publicly available
sequences or did not have metadata in which the authors were able to
share. After these filtering steps, the following studies remained: Ahn,
\emph{et al.} (11), Baxter, \emph{et al.} (12), Brim, \emph{et al.}
(29), Burns, \emph{et al.} (15), Chen, \emph{et al.} (13), Dejea,
\emph{et al.} (20), Flemer, \emph{et al.} (17), Geng, \emph{et al.}
(19), Hale, \emph{et al.} (27), Kostic, \emph{et al.} (43), Lu, \emph{et
al.} (26), Sanapareddy, \emph{et al.} (25), Wang, \emph{et al.} (14),
Weir, \emph{et al.} (23), and Zeller, \emph{et al.} (16). The Zackular
(44) study was not included because the 90 individuals analyzed within
the study are contained within the larger Baxter study (12). After
sequence processing, all the case samples for the Kostic study had 100
or less sequences remaining and was excluded, leaving a total of 14
studies that analysis could be completed on.

@@

\textbf{\emph{Sequence Processing:}} For the majority of studies, raw
sequences were downloaded from the Sequence Read Archive (SRA)
(\url{ftp://ftp-trace.ncbi.nih.gov/sra/sra-instant/reads/ByStudy/sra/SRP/})
and metadata were obtained by searching the respective accession number
of the study at the following website:
\url{http://www.ncbi.nlm.nih.gov/Traces/study/}. Of the studies that did
not have sequences and metadata on the SRA, data was obtained from DBGap
(n = 1, (11)) and directly from the authors (n = 4, (17, 23, 25, 27)).
Each study was processed using the mothur (v1.39.3) software program
(45) and quality filtering utilized the default methods for both 454 and
Illumina based sequencing. If it was not possible to use the defaults,
the stated quality cut-offs, from the study itself, were used instead.
Sequences that were made up of an artificial combination of two or more
different sequences and commonly known as chimeras were identified and
removed using VSEARCH (46) before \emph{de novo} OTU clustering at 97\%
similarity was completed using the OptiClust algorithm (47).

\textbf{\emph{Study Analysis Overview:}} OTU richness, evenness, and
Shannon diversity were first assessed for differences between controls,
adenoma tumors, and carcinoma turmors using both linear mixed-effect
models and ORs. For each individual study the Bray-Curtis index was used
to assess differences between control-adenoma and control-carcinoma
individuals. Next, all common genera were assessed for differences in
ORs for individuals having an adenoma or carcinoma and corrected for
multiple comparisons using the Benjamini-Hochberg method (48). We then
built Random Forest models based on all genera, all OTUs, or significant
OR taxa (only using taxa still significant after multiple comparison
correction). For both the full genera and significant OR taxa, models
were trained on one study then tested on the remaining studies using
genera-based relative abundances. The OTU-based models were built using
OTU level data and a 10-fold CV over 100 different iterations, based on
random 80/20 splitting of the data, was used to generate a range of
expected AUCs. This process was repeated for every study in the
meta-analysis. Comparisons of the initial trained model AUCs for the
full genera and significant OR taxa were made to the mean AUC generated
from the 100 different 10-fold CV runs of the respective OTU-based
model. For comparisons in which only control versus adenoma individuals
were made, the carcinoma individuals were excluded from each respective
study. Similarly, for comparisons in which control versus carcinoma
individuals were made the adenoma individuals were excluded from each
respective study. For all analysis completed fecal and tissue samples
were kept separate. Within the tissue groups the data were further
divided between samples from the same individual (matched) and those
from different individuals (unmatched).

@@

\textbf{\emph{Statistical Analysis:}} All statistical analysis after
sequence processing utilized the R (v3.4.3) software package (49). For
OTU richness, evenness, and Shannon diversity analysis, values were
power transformed using the rcompanion (v1.11.1) package (50) and then
Z-score normalized using the car (v2.1.6) package (51). Testing for OTU
richness, evenness, and Shannon diversity differences utilized linear
mixed-effect models created using the lme4 (v1.1.15) package (52) to
correct for study, repeat sampling of individuals (tissue only), and 16S
hyper-variable region used. Odds ratios (OR) were analyzed using both
the epiR (v0.9.93) and metafor (v2.0.0) packages (53, 54) by assessing
how many individuals with and without disease were above and below the
overall median value within each specific study. OR significance testing
utilized the chi-squared test. Diversity differences measured by the
Bray-Curtis index utilized the creation of distance matrix and testing
with PERMANOVA executed with the vegan (v2.4.5) package (55). Random
Forest models were built using both the caret (v6.0.78) and randomForest
(v4.6.12) packages (56, 57). All figures were created using both ggplot2
(v2.2.1) and gridExtra (v2.3) packages (58, 59).

@@

\hypertarget{ref-Sze2016}{}
38. \textbf{Sze, M. A.}, and \textbf{P. D. Schloss}. 2016. Looking for a
signal in the noise: Revisiting obesity and the microbiome. mBio.
American Society for Microbiology \textbf{7}:e01018--16.

\hypertarget{ref-Walters2014}{}
39. \textbf{Walters, W. A.}, \textbf{Z. Xu}, and \textbf{R. Knight}.
2014. Meta-analyses of human gut microbes associated with obesity and
IBD. FEBS Letters. Wiley-Blackwell \textbf{588}:4223--4233.

\hypertarget{ref-Finucane2014}{}
40. \textbf{Finucane, M. M.}, \textbf{T. J. Sharpton}, \textbf{T. J.
Laurent}, and \textbf{K. S. Pollard}. 2014. A taxonomic signature of
obesity in the microbiome? Getting to the guts of the matter. PLoS ONE.
Public Library of Science (PLoS) \textbf{9}:e84689.

\hypertarget{ref-keku_gastrointestinal_2015}{}
41. \textbf{Keku, T. O.}, \textbf{S. Dulal}, \textbf{A. Deveaux},
\textbf{B. Jovov}, and \textbf{X. Han}. 2015. The gastrointestinal
microbiota and colorectal cancer. American Journal of Physiology -
Gastrointestinal and Liver Physiology \textbf{308}:G351--G363.

\hypertarget{ref-vogtmann_epidemiologic_2016}{}
42. \textbf{Vogtmann, E.}, and \textbf{J. J. Goedert}. 2016.
Epidemiologic studies of the human microbiome and cancer. British
Journal of Cancer \textbf{114}:237--242.

\hypertarget{ref-kostic_genomic_2012}{}
43. \textbf{Kostic, A. D.}, \textbf{D. Gevers}, \textbf{C. S.
Pedamallu}, \textbf{M. Michaud}, \textbf{F. Duke}, \textbf{A. M. Earl},
\textbf{A. I. Ojesina}, \textbf{J. Jung}, \textbf{A. J. Bass},
\textbf{J. Tabernero}, \textbf{J. Baselga}, \textbf{C. Liu}, \textbf{R.
A. Shivdasani}, \textbf{S. Ogino}, \textbf{B. W. Birren}, \textbf{C.
Huttenhower}, \textbf{W. S. Garrett}, and \textbf{M. Meyerson}. 2012.
Genomic analysis identifies association of Fusobacterium with colorectal
carcinoma. Genome Research \textbf{22}:292--298.

\hypertarget{ref-zackular_human_2014}{}
44. \textbf{Zackular, J. P.}, \textbf{M. A. M. Rogers}, \textbf{M. T.
Ruffin}, and \textbf{P. D. Schloss}. 2014. The human gut microbiome as a
screening tool for colorectal cancer. Cancer Prevention Research
(Philadelphia, Pa.) \textbf{7}:1112--1121.

\hypertarget{ref-schloss_introducing_2009}{}
45. \textbf{Schloss, P. D.}, \textbf{S. L. Westcott}, \textbf{T.
Ryabin}, \textbf{J. R. Hall}, \textbf{M. Hartmann}, \textbf{E. B.
Hollister}, \textbf{R. A. Lesniewski}, \textbf{B. B. Oakley}, \textbf{D.
H. Parks}, \textbf{C. J. Robinson}, \textbf{J. W. Sahl}, \textbf{B.
Stres}, \textbf{G. G. Thallinger}, \textbf{D. J. Van Horn}, and
\textbf{C. F. Weber}. 2009. Introducing mothur: Open-Source,
Platform-Independent, Community-Supported Software for Describing and
Comparing Microbial Communities. Appl.Environ.Microbiol.
\textbf{75}:7537--7541.

\hypertarget{ref-rognes_vsearch_2016}{}
46. \textbf{Rognes, T.}, \textbf{T. Flouri}, \textbf{B. Nichols},
\textbf{C. Quince}, and \textbf{F. Mahé}. 2016. VSEARCH: A versatile
open source tool for metagenomics. PeerJ \textbf{4}:e2584.

\hypertarget{ref-westcott_opticlust_2017}{}
47. \textbf{Westcott, S. L.}, and \textbf{P. D. Schloss}. 2017.
OptiClust, an Improved Method for Assigning Amplicon-Based Sequence Data
to Operational Taxonomic Units. mSphere \textbf{2}.

\hypertarget{ref-benjamini_controlling_1995}{}
48. \textbf{Benjamini, Y.}, and \textbf{Y. Hochberg}. 1995. Controlling
the false discovery rate: A practical and powerful approach to multiple
testing. Journal of the Royal Statistical Society. Series B
(Methodological) \textbf{57}:289--300.

\hypertarget{ref-r_citation_2017}{}
49. \textbf{R Core Team}. 2017. R: A language and environment for
statistical computing. R Foundation for Statistical Computing, Vienna,
Austria.

\hypertarget{ref-rcompanion_citation_2017}{}
50. \textbf{Mangiafico, S.} 2017. Rcompanion: Functions to support
extension education program evaluation.

\hypertarget{ref-car_citation_2011}{}
51. \textbf{Fox, J.}, and \textbf{S. Weisberg}. 2011. An R companion to
applied regressionSecond. Sage, Thousand Oaks CA.

\hypertarget{ref-lme4_citation_2015}{}
52. \textbf{Bates, D.}, \textbf{M. Mächler}, \textbf{B. Bolker}, and
\textbf{S. Walker}. 2015. Fitting linear mixed-effects models using
lme4. Journal of Statistical Software \textbf{67}:1--48.

\hypertarget{ref-epir_citation_2017}{}
53. \textbf{Telmo Nunes, M. S. with contributions from}, \textbf{C.
Heuer}, \textbf{J. Marshall}, \textbf{J. Sanchez}, \textbf{R. Thornton},
\textbf{J. Reiczigel}, \textbf{J. Robison-Cox}, \textbf{P. Sebastiani},
\textbf{P. Solymos}, \textbf{K. Yoshida}, \textbf{G. Jones}, \textbf{S.
Pirikahu}, \textbf{S. Firestone}, and \textbf{R. Kyle.} 2017. EpiR:
Tools for the analysis of epidemiological data.

\hypertarget{ref-metafor_citation_2010}{}
54. \textbf{Viechtbauer, W.} 2010. Conducting meta-analyses in R with
the metafor package. Journal of Statistical Software \textbf{36}:1--48.

\hypertarget{ref-vegan_citation_2017}{}
55. \textbf{Oksanen, J.}, \textbf{F. G. Blanchet}, \textbf{M. Friendly},
\textbf{R. Kindt}, \textbf{P. Legendre}, \textbf{D. McGlinn}, \textbf{P.
R. Minchin}, \textbf{R. B. O'Hara}, \textbf{G. L. Simpson}, \textbf{P.
Solymos}, \textbf{M. H. H. Stevens}, \textbf{E. Szoecs}, and \textbf{H.
Wagner}. 2017. Vegan: Community ecology package.

\hypertarget{ref-caret_citation_2017}{}
56. \textbf{Jed Wing, M. K. C. from}, \textbf{S. Weston}, \textbf{A.
Williams}, \textbf{C. Keefer}, \textbf{A. Engelhardt}, \textbf{T.
Cooper}, \textbf{Z. Mayer}, \textbf{B. Kenkel}, \textbf{the R Core
Team}, \textbf{M. Benesty}, \textbf{R. Lescarbeau}, \textbf{A. Ziem},
\textbf{L. Scrucca}, \textbf{Y. Tang}, \textbf{C. Candan}, and
\textbf{T. Hunt.} 2017. Caret: Classification and regression training.

\hypertarget{ref-randomforest_citation_2002}{}
57. \textbf{Liaw, A.}, and \textbf{M. Wiener}. 2002. Classification and
regression by randomForest. R News \textbf{2}:18--22.

\hypertarget{ref-ggplot2_citation_2009}{}
58. \textbf{Wickham, H.} 2009. Ggplot2: Elegant graphics for data
analysis. Springer-Verlag New York.

\hypertarget{ref-gridextra_citation_2017}{}
59. \textbf{Auguie, B.} 2017. GridExtra: Miscellaneous functions for
``grid'' graphics.
